Quantum Algorithms for Portflolio Optimisation in Finance

### 2024-05-09 project/paper-v2.tex
update .gitignore file
update paper
update project paper

In the Modern Portfolio Theory proposed by Markowistz \cite{Wilmott2007}, the goal of portfolio optimisation is to find the best combination of assets that maximises the return for a given level of risk and some constraints. This is a highly constrained quadratic optimisation problem which can be formulated in several ways depending on the conditions of the 
investor \cite{Herman2022}. Machine Learning based models (ML) such as the one proposed by Mazumdar et al. \cite{Mazumdar2020} are widely used for minimising risk contributors and maximising asset diversification.

@@

@@

\bibliography{./references-2.bib}

>>>>

In the Modern Portfolio Theory proposed by Markowistz \cite{Wilmott2007}, the goal of portfolio optimisation is to find the best combination of assets that maximises the return for a given level of risk and some constraints. This is a highly constrained quadratic optimisation problem, known to be NP-Hard, which can be formulated in several ways depending on the conditions of the 
investor \cite{Herman2022}. Machine Learning based models (ML) such as the one proposed by Mazumdar et al. \cite{Mazumdar2020} are widely used for minimising risk contributors and maximising asset diversification.

@@

Although this work is focused on two financial applications, the quantum algorithms reviewed here can be applied to a wide range of financial problems. In recent years, important surveys have been published on the topic of quantum computing in finance \cite{Orus2019,Egger2020a,Albareti2022,Herman2022,Herman2023} 
and we refer the interested readers to these works for a more comprehensive overview of the field.

@@

\bibliography{/home/pacman/Documents/git-repositories/quantum-computing/lecture-notes/bibliography.bib}
